---
title: "Project Proposal"
author:
  - "Dean Heilig"
  - "Felix Leitner"
date: today
---

## **Dataset**

**Source:** <https://www.kaggle.com/datasets/laveshjadon/ai-impact-on-students>

**Licence:** [CC0: Public Domain](https://creativecommons.org/publicdomain/zero/1.0/) Official licencing description: "You can copy, modify, distribute and perform the work, even for commercial purposes, all without asking permission."

**Description:** First of all, it is important to note that this is a **synthetic dataset**, so we won’t be able to draw any real-world conclusions from our analysis. The dataset explores the impact, extent, and results of AI usage on students across many indicators such as student major, whether they have a paid subscription or not, pre- and post-semester GPA, and skill retention. Overall, this dataset includes data about 50,000 students across 15 indicators.

Research Questions

1.  Does a paid subscription impact the improvement (or decline) of a student’s GPA?

    Needed columns: Post_Semester_GPA, Pre_Semester_GPA (difference), Paid_Subscription

    This question is explanatory but not causal. A possible improvement could have many reasons, such as higher dedication to studying among paying students.

2.  Which majors’ average GPA is most positively and negatively influenced by AI usage? And is this effect related to the fraction of time spent studying with AI compared to studying without AI?

    Needed columns: Major_Category, Post_Semester_GPA, Pre_Semester_GPA, Weekly_GenAI_Hours, Traditional_Study_Hours

    This question is explanatory but not causal. Differences between majors could also be caused by other factors, such as exam formats.

## **Context and target audience**

Due to this dataset being synthetic, the results have no real-world relevance. However, the same analytical approach could still be useful if applied to a real dataset, where the results might be of interest in both academic and private contexts.

The analysis could be relevant in both an academic and private context. In an academic context, it would be interesting to identify possible reasons behind correlations. For students, it could be beneficial to see trends in their own field of study in order to understand whether AI is more likely to be associated with positive or negative differences in academic performance. A short summary with the possibility of a deeper dive would therefore be the best presentation format to satisfy both target audiences.

## **Initial data analysis**

```{r}
#| label: load-data and libraries
#| include: false
library(tidyverse)
library(here)

data_raw <- read_csv(here("data", "raw", "ai_student_impact.csv"))
```

```{r}
#| echo: false
glimpse(data_raw)
```

```{r}
data_raw %>%
  dplyr::select(Post_Semester_GPA, Pre_Semester_GPA, Paid_Subscription, Major_Category, Weekly_GenAI_Hours, Traditional_Study_Hours) %>%
  summary()
```

**Plot 1 — Distribution of the outcome variable:**

```{r}
data_raw %>%
  ggplot(aes(x = Post_Semester_GPA)) +
  geom_histogram(bins = 30) +
  labs(
    title = "Distribution of Post-Semester GPA",
    x = "Post-Semester GPA",
    y = "Count"
  )
```

**Plot 2 — Relationship or trend relevant to a research question:**

```{r}
data_raw %>%
  filter(Major_Category == "STEM") %>%
  slice_sample(n = 1000) %>%
  ggplot(aes(x = Weekly_GenAI_Hours, y = Post_Semester_GPA)) +
  geom_point(alpha = 0.6) +
  labs(
    title = "Relationship between Post-Semester GPA and Hours Spent Studying with AI",
    x = "Weekly GenAI Hours",
    y = "Post-Semester GPA",
  )
```

**Data quality issues:**

-   Synthetic dataset → no real-world conclusions can be drawn. Creating a package with the functions used for the analysis would be useful if a real dataset with similar indicators becomes available in the future.

-   At first glance, all indicators seem to be reasonably generated, with the exception of **Post_Semester_GPA**. As shown in the plot, there are too many top GPAs, so additional filtering may be required.

## **Analysis Plan**

-   *Which variables will you use?*

    As mentioned before: Post_Semester_GPA, Pre_Semester_GPA, Paid_Subscription, Major_Category, Weekly_GenAI_Hours, Traditional_Study_Hours

-   *What analytical approach or method seems appropriate, and why?*

    1.  A boxplot of the GPA difference (Post_Semester_GPA - Pre_Semester_GPA) for students with and without a paid subscription could provide a useful overview. A linear regression model (GPA Difference \~ Paid_Subscription) could be used for further investigation.
    2.  A boxplot of the GPA difference for each major could help answer the first part of the question by comparing average performance changes across majors. For the second part, a multiple linear regression model such as GPA Difference \~ Major_Category + AI_Study_Fraction (Weekly_GenAI_Hours / Traditional_Study_Hours) could be appropriate.

-   *What cleaning or transformation steps do you anticipate needing?*

    Some columns need to be transformed into (ordered) factors, as already done in the practical. In addition, a GPA difference variable (Post_Semester_GPA - Pre_Semester_GPA) and an AI study fraction variable (Weekly_GenAI_Hours/ Traditional_Study_Hours) will likely be needed. Standard data analysis steps such as grouping, summarising and plotting will also be required.

-   *What are the main uncertainties or risks (e.g. not enough data, confounding variables, missing values)?*

    Unclear or useless results due to the dataset being synthetic.

## **Workflow organisation**

-   *Code style:* We will follow the coding style taught in StatProg1 and StatProg2, including the use of the tidyverse style with piping (%\>%), the here package for file paths, and other conventions. We will enforce this using a code_style.md file, which documents used packages and coding style conventions.

-   *Packages:* tidyverse, janitor, here, ...

-   *Git workflow:* There will always be at least two branches to avoid conflicts within the group. This, together with a clear separation of tasks, should help to prevent merge conflicts. We will also work on separate .qmd files, which will later be combined into a final document using the include command for additional modularity.

-   *`.gitignore`:* 

    .Rhistory .RData .Rproj.user/

    /.quarto/ \_site/

    .DS_Store Thumbs.db

    \*\*/\*.quarto_ipynb

    ...
