**Original Research Question:** Does education level influence the proportion of the population across different countries and age groups that use the internet daily or almost every day within the last quarter of the year? (From 2021-2025)

**Original Analysis Plan:** First of all, we would use a boxplot to get a first insight into the relationship between education level and daily or almost daily internet usage. Using faceted plots, we are able to compare these results across different countries and age groups. Then, a linear model could be used to further examine the impact of age, education level, and country.

```{r}
library(tidyverse)
library(here)
library(gt)
library(broom)
library(scales)
```

```{r}
data = read_csv(here("data", "processed", "ICT_data_clean.csv"))
```

**Dataset Preparation:**

```{r}
data = data %>%
  filter(EDUCATION_LEVEL != "Total") %>%
  filter(UNIT_MEASURE == "PT_POP") %>%
  filter(MEASURE == "C5B1_I") %>%
  filter(SEX == "Total") %>%
  filter(AGE != "Y16T74") %>%
  select(-INCOME_GROUP, -EMP_STATUS, -BREAKDOWN_V7_HH, -`V7 Breakdowns households`, -REF_AREA) %>%
  mutate(
    EDUCATION_LEVEL = factor(EDUCATION_LEVEL, levels = c("LO", "ME", "HI")),
    AGE = factor(AGE, levels = c("Y16T24", "Y25T54", "Y55T74"))
    )
```

There were no observations for the USA for the required combination of variables. Therefore, we removed the comparison between countries from the research question. We also decided to remove the comparison across years for two reasons: first, to narrow the scope of the research question, and second, because temporal trends are better addressed in a separate research question and analysis.

**New Research Question:** Is education level associated with the proportion of the population that uses the internet daily or almost every day within different age groups?

In order to address the revised research question, we slightly adjust our analysis plan. Two main changes were made: `TIME_PERIOD` and `REF_AREA` are no longer included in either the plot or the linear model.

**New analysis plan:** We will regress `OBS_VALUE` (the share of the population using the internet daily or almost every day) on `EDUCATION_LEVEL`, `AGE`, and their interaction using linear regression. We will report a coefficient table with confidence intervals and a boxplot with `AGE` as facet. This addresses RQ1 because it quantifies the association between education level and daily internet use and assesses whether this association differs across age groups.

**Coefficient table:**

```{r}
data_lm = data

data_lm$EDUCATION_LEVEL <- relevel(factor(data_lm$EDUCATION_LEVEL), ref = "ME")
data_lm$AGE <- relevel(factor(data_lm$AGE), ref = "Y25T54")

linear_model = lm(OBS_VALUE ~ EDUCATION_LEVEL * AGE, data = data_lm)
# summary(linear_model)

tidy(linear_model, conf.int = TRUE) %>%
  gt() %>%
    fmt_number(decimals = 2) %>%
    fmt_number(p.value, decimals = 3) %>%
    cols_label(
      term = "Term",
      estimate = "Estimate",
      std.error = "Std. Error",
      statistic = "Statistic",
      p.value = "P-Value",
      conf.low = "Conf. Low",
      conf.high = "Conf. High"
    ) %>%
    cols_align(align = "right", columns = where(is.numeric)) %>%
    tab_header(
      title = "Linear regression results",
      subtitle = "Coefficient table"
    ) %>%
    tab_source_note("Source: OECD ICT Access and Usage by Individuals")
```

Instead of modelling `OBS_VALUE ~ EDUCATION_LEVEL + AGE`, we chose `OBS_VALUE ~ EDUCATION_LEVEL * AGE`. The interaction term allows the relationship between education level and daily or almost daily internet use to vary across age groups, rather than assuming that the effect of education is the same for all age groups. This enables us to assess whether differences in internet use between education levels become larger or smaller depending on age, which is directly relevant to our research question.

**Interpretation:**

**Box-Plot:**

```{r}
data_plot = data %>%
  mutate(EDUCATION_LEVEL = fct_recode(EDUCATION_LEVEL,
                                      "High" = "HI",
                                      "Medium" = "ME",
                                      "Low" = "LO"
                                      )
         ) %>%
  mutate(AGE = fct_recode(AGE,
                          "55 - 74" = "Y55T74",
                          "25 - 54" = "Y25T54",
                          "16 - 24" = "Y16T24"
                          )
         )
#| fig-alt: "Boxplots comparing daily internet use across low, medium, and high education levels for three age groups (16–24, 25–54, and 55–74 years). Daily internet use generally increases with education level in every age group, and the differences between education levels become larger in older age groups."
plot = data_plot %>%
  ggplot(
    aes(x = factor(EDUCATION_LEVEL),
        y = OBS_VALUE)
  ) + 
  geom_boxplot() +
  facet_wrap(~ AGE) +
  theme_bw() +
  labs(
    y = "Part of the population",
    x = "Education level",
    title = "Daily or almost daily internet use by education level across age groups",
    subtitle = "Daily internet use tends to increase with education level in all age groups,\nwith larger differences observed among older age groups.",
    caption = "Source: OECD ICT Access and Usage by Individuals",
  ) +
  scale_y_continuous(
    labels = label_number(suffix = "%"))

plot
```

**Interpretation:**
